Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-06-21 supp_mat_complexity_selection.Rmd
Revised plots of multivariate fitness landscapes for manuscript.

  get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

@@

  absolute_fitness_df <- data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model), 
                    lower = get_intervals_absolute_fitness[1, ],
                    upper = get_intervals_absolute_fitness[2, ],
                    t(get_bootstraps_absolute_fitness$t))

@@

  get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

@@

  relative_fitness_df <- data.frame(newdata, 
                    average = get_relative_fitness(logistic_model), 
                    lower = get_intervals_relative_fitness[1, ],
                    upper = get_intervals_relative_fitness[2, ],
                    t(get_bootstraps_relative_fitness$t))
  # Organize data
  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
}
```

@@

>>>>

  if(is.null(bootstraps) == FALSE){
    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

@@

  absolute_fitness_df <- data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model), 
                    lower = get_intervals_absolute_fitness[1, ],
                    upper = get_intervals_absolute_fitness[2, ],
                    t(get_bootstraps_absolute_fitness$t))
  } else {
    absolute_fitness_df <- data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model))
  }

@@

  if(is.null(bootstraps) == FALSE){
    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

@@

  relative_fitness_df <- data.frame(newdata, 
                    average = get_relative_fitness(logistic_model), 
                    lower = get_intervals_relative_fitness[1, ],
                    upper = get_intervals_relative_fitness[2, ],
                    t(get_bootstraps_relative_fitness$t))
  } else {
      relative_fitness_df <- data.frame(newdata, 
                    average = get_relative_fitness(logistic_model))
  }

  # Organize data
  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
}
```

@@

```{r Multivariate Landscapes}

## Clutch size x Female preference ----

# Control
RF_control_clutch.x.preference <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = seq(-1,1,length.out=1000), 
     sc.female_preference = seq(-1,1,length.out=1000)), 
  bootstraps=NULL)

# Treatment
RF_treatment_clutch.x.preference <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = seq(-1,1,length.out=1000),
     sc.female_preference = seq(-1,1,length.out=1000)), 
  bootstraps=NULL)

## Gall size x Clutch size ----

# Control
RF_control_size.x.clutch <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = seq(-1,1,length.out=1000),
     sc.clutch_size = seq(-1,1,length.out=1000), 
     sc.female_preference = 0), 
  bootstraps=NULL)

# Treatment
RF_treatment_size.x.clutch <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = seq(-1,1,length.out=1000),
     sc.clutch_size = seq(-1,1,length.out=1000),
     sc.female_preference = 0), 
  bootstraps=NULL)

## Gall size x Female preference ----

# Control
RF_control_size.x.preference <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = seq(-1,1,length.out=1000),
     sc.clutch_size = 0, 
     sc.female_preference = seq(-1,1,length.out=1000)), 
  bootstraps=NULL)

# Treatment
RF_treatment_size.x.preference <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = seq(-1,1,length.out=1000),
     sc.clutch_size = 0,
     sc.female_preference = seq(-1,1,length.out=1000)), 
  bootstraps=NULL)

## Relative fitness plots ----

# Get range in relative fitness for accurate scaling across all plots
RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
  summarise(min = min(average), max = max(average))

# Clutch x Preference
RF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch.x.preference$relative_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Female preference (SDs)") +
  ylab("Clutch size (SDs)") +
  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")

# Size x Clutch
RF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_size.x.clutch$relative_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")

# Size x Preference
RF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_size.x.preference$relative_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Gall diameter (SDs)") +
  ylab("Female preference (SDs)") +
  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")

# Get legend
RF_landscape_legend <- get_legend(RF_plot_size.x.preference)

# Format plots
RF_landscape_plots <- plot_grid(
  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
  RF_plot_size.x.preference + theme(legend.position = "none"), 
  nrow=2, align="hv", labels = "AUTO")
RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
RF_landscape_2d
save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)

## Absolute fitness landscapes ----
AF_range <- bind_rows(RF_treatment_clutch.x.preference$absolute_fitness, RF_control_clutch.x.preference$absolute_fitness,
          RF_treatment_size.x.clutch$absolute_fitness, RF_control_size.x.clutch$absolute_fitness,
          RF_treatment_size.x.preference$absolute_fitness, RF_control_size.x.preference$absolute_fitness) %>%
  summarise(min = min(average), max = max(average))

# Size x Preference
AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Gall diameter (SDs)") +
  ylab("Female preference (SDs)") +
  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")

# Size x Clutch
AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")

# Clutch x Preference
AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Female preference (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")

# Get legend
AF_landscape_legend <- get_legend(AF_plot_size.x.preference)

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
  AF_plot_size.x.preference + theme(legend.position = "none"), 
  nrow=2, align="hv", labels = "AUTO")
AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
AF_landscape_2d
save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
```
